Predicting Solid State Material Platforms for Quantum Technologies

### 2022-02-03 paper_v2.tex
Updates from Overleaf

Four well-tested machine learning algorithms were employed in this work: logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009}. 
These four machine learning methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above. %This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.

@@

%OH: Øyvind og Seb: 
%Comment on pitfalls of ML metods
%Comment on pitfalls on data size.

@@

%empirical approach
The empirical approach differs in many aspects from the Ferrenti and extended Ferrenti approaches. 
Firstly, for the empirical approach, the gradient boosting model performs optimally at $13$ principal components with a mean F$1$-score of $0.96$. 
We find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively. Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.   
Secondly, the first principal component is by far the most important feature for all models in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b). 
This is part of the reason why we experience a large accuracy for only a single feature (see also the Supplementary Material at \cite{supplementary} fur further details). The first principal component's corresponding features is a complex combination of several material properties, but we find that it includes bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system. 
The standard deviation of the radial distribution function appears multiple times in the list of features and appears to be of particular importance. 
Thirdly, the empirical approach differs in how much explained variation is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti  and $11 \ \%$ for the extended Ferrenti approach. We find the difference striking considering that the approaches share the same ultimate goal, but where the training sets apparently exhibit large and significant variations.

>>>>

Four well-tested machine learning algorithms were employed in this work: logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009}. 
These four machine learning methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above. This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.

@@

%Beneficial to use simple ML-methods for small datasets, since more advanced methods need (ALOT) more data to perform good
The three approaches define labelled data of varying size, where the smallest is from the empirical approach. For small datasets, it is proven beneficial to repeat the cross-validation, as this is a method that allows us to measure the stability of the predictions given against pertubations (i.e. few different entries) of the training data \cite{Beleites2008}.

@@

%empirical approach
% OH: This paragraph is a duplicate from supplementary
The empirical approach differs in many aspects from the Ferrenti and extended Ferrenti approaches. 
%Firstly, for the empirical approach, the gradient boosting model performs optimally at $13$ principal components with a mean F$1$-score of $0.96$. 
Firstly, We find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively. Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.   
Secondly, the first principal component is by far the most important feature for all models in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b). 
This is part of the reason why we experience a large accuracy for only a single feature (see also the Supplementary Material at \cite{supplementary} for further details). The first principal component's corresponding features is a complex combination of several material properties, but we find that it includes bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system. 
The standard deviation of the radial distribution function appears multiple times in the list of features and appears to be of particular importance. 
Thirdly, the empirical approach differs in how much explained variation is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti  and $11 \ \%$ for the extended Ferrenti approach. We find the difference striking considering that the approaches share the same ultimate goal, but where the training sets apparently exhibit large and significant variations.
